---
title: "HW1"
output:
  pdf_document: default
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Homework1
> Group 10 (Zili Huang, Jiabo Cheng)

## Problem 1 (Forest Fires)
### a)
```{r a, echo=TRUE}
ff_f<- read.csv("forestfires.csv")
library(ggplot2)
p1 <- ggplot(ff_f) + geom_point(aes(x = temp, y = area), colour = "black", alpha = 0.5) + ggtitle("area vs. temp")
p2 <- ggplot(ff_f) + geom_point(aes(x = month, y = area), colour = "black", alpha = 0.5) + ggtitle("area vs month")
p3 <- ggplot(ff_f) + geom_point(aes(x = DC, y = area), colour = "black", alpha = 0.5) + ggtitle("area vs DC")
p4 <- ggplot(ff_f) + geom_point(aes(x = RH, y = area), colour = "black", alpha = 0.5) + ggtitle("area vs RH")
library(gridExtra)
grid.arrange(p1,p2, p3, p4, nrow=2)
```

### b)

```{r b}
ggplot(ff_f) + geom_histogram(aes(x = wind),binwidth = 1, alpha = 0.8,colour = "black", fill = "lightblue")+ labs(title = "Histogram of wind speed(km/h)", x = "Wind Speed(km/h)", y = "Density")
```

### c)
```{r c}
 summary(ff_f$wind)
```

### d)
```{r d}
 ggplot(ff_f) + geom_histogram(aes(x = wind,y = ..density..),binwidth = 1, alpha = 0.8, colour = "black", fill = "white")+ labs(title = "Histogram of wind speed(km/h)", x = "Wind Speed(km/h)", y = "Density") + geom_density(aes(x= wind),alpha = 0.3, fill = "pink")
```

### e)
```{r e}
ggplot(ff_f, aes(wind))+ geom_density(aes(fill = factor(month)),alpha=.3)+ labs(title = "Density of wind speed by month(km/h)", x = "Wind Speed(km/h)", y = "Density", fill = "Month")
```

### f)
```{r f}
library(GGally)
ggpairs(ff_f[, c("temp","RH","DC","DMC")])
```

> Based on the plots above, the temp and RH has negative linear relationship, the temp and DC, temp and DMC, DC and DMC have positive linear relationship.

### g)
```{r g}
p1 <- ggplot(ff_f) + geom_boxplot(aes(y= temp))
p2 <- ggplot(ff_f) + geom_boxplot(aes(y= ISI))
p3 <- ggplot(ff_f) + geom_boxplot(aes(y= DC))
grid.arrange(p1,p2, p3,  nrow=1)
```

> All the boxplots have outliers. Since all of them have large ranges. 

### h)
```{r h}
p1 <- ggplot(ff_f) + geom_histogram(aes(x = DMC), alpha = 0.8,colour = "black", fill = "lightblue") + labs(title = "Histogram of DMC", x = "DMC", y = "Frequency")
p2 <- ggplot(ff_f) + geom_histogram(aes(x = DMC), alpha = 0.8,colour = "black", fill = "lightblue") + scale_x_log10() + labs(title = "Histogram of log of DMC", x = "log of DMC", y = "Frequency")
grid.arrange(p1,p2, nrow = 1)
 
```

> The distribution of log of DMC seems like a normal distribution.

## Problem 2 (Twitter Accounts)
### a)
```{r a2}
tw_f <- read.csv("M01_quasi_twitter.csv")
ggplot(tw_f) + geom_histogram(aes(x= friends_count)) + labs(title = "Density of the friends count")
ggplot(tw_f) + geom_boxplot(aes(y = friends_count)) + labs(title = "Boxplot of the friends count")
```

> Most of data of frends_count are concentrate on the left of the plot.

### b)
```{r b2}
summary(tw_f$friends_count)
```

### c)
```{r c2}
```

> I believe the quality of the friend_count data is poor. Since there're too many outliers which make analyzation hard. 

### d)
```{r d2}
library("scatterplot3d")
scatterplot3d(tw_f$created_at_year, tw_f$education, tw_f$age, main = "3D Scatter Plot", xlab = "Created at year", ylab = "Education", zlab = "Age", color = "steelblue")
```

### e)
```{r e2}
par(mfcol=c(1,2))
ac <- c(650,1000,900,300,14900)
ct <- c("UK","Canada","India","Australia","US")
label <- paste(ct, " ", round(ac/sum(ac)*100), "%", sep="")
pie(ac,labels = label, main = "Pie chart")

library("plotrix")
pie3D(ac, labels = label, main = "3D Pie chart", col = c("bisque","pink","aquamarine2","white","lightblue"))
```

### f)
```{r f2}
ggplot(tw_f) + geom_density(aes(x= created_at_year), alpha = 0.3, fill = "pink") +labs(title = "Kernel density plot of created at year", x = "Created at Year", y = "Density")
```

> We could easily found the first year of most account created is 2009, and the second is 2014.


## Problem 3
### a)
```{r a3}
rd_f <- read.csv("raw_data.csv")
Ndata <- data.frame(scale(rd_f))
```

### b)
```{r b3}
p1 <- ggplot(rd_f) + geom_boxplot(aes(y = A))
p2 <- ggplot(rd_f) + geom_boxplot(aes(y = B))
p3 <- ggplot(rd_f) + geom_boxplot(aes(y = C))
p4 <- ggplot(rd_f) + geom_boxplot(aes(y = D))
grid.arrange(p1,p2,p3,p4, ncol=4)
```

### c)
```{r c3}
p1 <- ggplot(Ndata) + geom_boxplot(aes(y = A))
p2 <- ggplot(Ndata) + geom_boxplot(aes(y = B))
p3 <- ggplot(Ndata) + geom_boxplot(aes(y = C))
p4 <- ggplot(Ndata) + geom_boxplot(aes(y = D))
grid.arrange(p1,p2,p3,p4, ncol=4)
```

### d)
```{r d3}
 
```

> After the standardization, it would be easier to compare the variables in the dataset,......


### e)
```{r e3}
ggpairs(rd_f[, c("A","B")])
 
```

> There's no correlation between A and B.
